\begin{thebibliography}{99}
\addcontentsline{toc}{chapter}{\bibname}

\bibitem{Flash}
	Introducing the Adobe Flash Platform. Adobe, July 2011.\\
	\url{http://www.adobe.com/devnet/flashplatform/articles/flashplatform\_overview.html}
	
\bibitem{JavaApplets}
	Java applet. Wikipedia, 2013.\\
	\url{http://en.wikipedia.org/wiki/Java\_applet}
	
\bibitem{JavaScript}
	JavaScript. Wikipedia, 2013.\\
	\url{http://en.wikipedia.org/wiki/JavaScript}
	
\bibitem{EcmaScript}
	ECMAScript Language Specification. Ecma International, June 2011.\\
	\url{http://www.ecma-international.org/publications/files/ECMA-ST/Ecma-262.pdf}
	
\bibitem{Ajax}
	{\sc Garrett,} Jesse James.\\ Ajax: A New Approach to Web Applications. Adaptive Path, February 2005.\\
	\url{http://www.adaptivepath.com/ideas/ajax-new-approach-web-applications}

\bibitem{Html5}
	HTML5 Introduction. W3schools, 2013.\\
	\url{http://www.w3schools.com/html/html5\_intro.asp}

\bibitem{Backends}
  {\sc Ashkenas,} Jeremy. List of languages that compile to JS. July 2013.\\
  \url{https://github.com/jashkenas/coffee-script/wiki/List-of-languages-that-compile-to-JS}
	
\bibitem{Meijer}
	{\sc Meijer,} Erik and {\sc Drayton,} Peter. Static Typing Where Possible, Dynamic Typing When Needed: The End of the Cold War Between Programming Languages. Microsoft Research 2004.\\
	\url{http://research.microsoft.com/en-us/um/people/emeijer/Papers/RDL04Meijer.pdf}
	
\bibitem{RequireJs}
	RequireJS.\\
	\url{http://requirejs.org/}
	
\bibitem{HeadJs}
	HeadJS.\\
	\url{http://headjs.com/}
	
\bibitem{JsLint}
	JSLint, The JavaScript Code Quality Tool.\\
	\url{http://www.jslint.com/}
	
\bibitem{JsHint}
	JSHint, a JavaScript Code Quality Tool.\\
	\url{http://www.jshint.com/}

\bibitem{GoogleClosure}
	Google Closure Compiler.\\
	\url{http://closure-compiler.appspot.com/home}
	
\bibitem{Dart}
	Dart: Structured web apps.\\
	\url{http://www.dartlang.org/}
	
\bibitem{CoffeeScript}
	CoffeeScript.\\
	\url{http://coffeescript.org/}
	
\bibitem{TypeScript}
	TypeScript.\\
	\url{www.typescriptlang.org/}
	
\bibitem{NodeJs}
	node.js\\
	\url{http://nodejs.org/}
	
\bibitem{Rpc}
	Remote procedure call. Wikipedia 2013.\\
	\url{http://en.wikipedia.org/wiki/Remote\_procedure\_call}
	
\bibitem{Gwt}
	GWT Project.\\
	\url{www.gwtproject.org/}
	
\bibitem{SharpKit}
	SharpKit - C\# to JavaScript Compiler.\\
	\url{http://sharpkit.net/}
	
\bibitem{Tiobe}
	TIOBE Programming Community Index for July 2013. Tiobe, 2013.\\
	\url{http://www.tiobe.com/index.php/content/paperinfo/tpci/index.html}
	
\bibitem{Dom}
	Document Object Model (DOM) Specifications. W3C 2004.\\
	\url{http://www.w3.org/DOM/DOMTR}
		
\bibitem{Jquery}
	jQuery.\\
	\url{http://jquery.com/}
	
\bibitem{Sbt}
	Scala Build Tool.\\
	\url{http://www.scala-sbt.org/}
	
\bibitem{Play}
	Play.\\
	\url{http://www.playframework.com/}
	
\bibitem{Typesafe}
	Typesafe.\\
	\url{http://typesafe.com/}
	
\bibitem{Self}
	Self.\\
	\url{http://selflanguage.org/}
	
\bibitem{ScalableComponents}
	{\sc Odersky,} Martin and {\sc Zenger,} Matthias. Scalable Component Abstractions. Proc. OOPSLA 2005.\\
	\url{http://lampwww.epfl.ch/~odersky/papers/ScalableComponent.pdf}
	
\bibitem{Linq}
  LINQ (Language-Integrated Query). MSDN 2013.\\
  \url{http://msdn.microsoft.com/en-us/library/vstudio/bb397926.aspx}
	
\bibitem{ScalaProgramming}
	{\sc Odersky,} Martin and {\sc Spoon,} Lex and {\sc Venners,} Bill.  Programming in Scala, Second Edition. Artima, 2010
	
\bibitem{ScalaAdvancedTypes}
	Advantages of Scala's Type System. StackOverflow 2013.\\
	\url{http://stackoverflow.com/questions/3112725/advantages-of-scalas-type-system}
	
\bibitem{Linearization}
  {\sc McBeath}, Jim. Scala Class Linearization. Coding and Life, 2010.\\
	\url{http://jim-mcbeath.blogspot.cz/2009/08/scala-class-linearization.html}
	
\bibitem{Reflection}
	Symbols, Trees, and Types. Scala Documentation 2013.\\
	\url{http://docs.scala-lang.org/overviews/reflection/symbols-trees-types.html}
	
\bibitem{SourceMaps}
  {\sc Seddon,} Ryan. Introduction to JavaScript Source Maps. HTML5 Rocks, March 2012.\\
  \url{http://www.html5rocks.com/en/tutorials/developertools/sourcemaps/}
	
\bibitem{W3c}
  World Wide Web Consortium.\\
	\url{http://www.w3.org/}
	
\bibitem{ScalaDynamic}
  Scala Dynamic. Scala API Documentation 2013.\\
	\url{http://www.scala-lang.org/api/current/index.html\#scala.Dynamic}
	
\bibitem{ScalaLibrary}
	Scala Standard Library API. Scala API Documentation 2013.\\
  \url{http://www.scala-lang.org/api/current/index.html\#package}
	
\bibitem{Lazy}
  Lazy initialization. Wikipedia 2013.\\
	\url{http://en.wikipedia.org/wiki/Lazy\_initialization}
	
\bibitem{CompilerPlugins}
  {\sc Spoon,} Lex. Writing Scala Compiler Plugins. Scala 2009.\\
  \url{http://www.scala-lang.org/node/140}
	
\bibitem{ScalaFutures}
  Futures and Promises. Scala Documentation 2013.\\
  \url{http://docs.scala-lang.org/overviews/core/futures.html}
	
\bibitem{ScalaGwt}
  Scala+GWT Project.\\
  \url{https://github.com/scalagwt}
	
\bibitem{S2js}
  S2JS Compiler Plugin.\\
  \url{https://github.com/alvaroc1/s2js}
	
\bibitem{Scalosure}
  Scalosure.\\
  \url{https://github.com/efleming969/scalosure}
	
\bibitem{JsScala}
  js.scala: JavaScript as an embedded DSL in Scala.\\
  \url{https://github.com/js-scala/js-scala}
	
\bibitem{ScalaJs}
  Scala.js, a Scala to JavaScript compiler.\\
  \url{https://github.com/sjrd/scala-js}
	
\bibitem{WebWorkers}
  Using web workers. Mozilla Developer Network 2013.\\
  \url{https://developer.mozilla.org/en-US/docs/Web/Guide/Performance/Using\_web\_workers}
	
\bibitem{Actors}
  Actor Model. Wikipedia 2013.\\
  \url{http://en.wikipedia.org/wiki/Actor\_model}
	
\bibitem{Akka}
	Akka.\\
	\url{http://akka.io/}
	
\bibitem{WebSockets}
  {\sc Ubl}, Malte and {\sc Kitamura} Eiji. Introducing WebSockets: Bringing Sockets to the Web. HTML5 Rocks, Octomber 2010.\\
	\url{http://www.html5rocks.com/en/tutorials/websockets/basics/}
	
\bibitem{StringInterpolation}
	{\sc Suereth} Josh. String Interpolation. Scala Documentation 2013.\\
	\url{http://docs.scala-lang.org/overviews/core/string-interpolation.html}
	
\bibitem{Equality}
  {\sc Odersky,} Martin and {\sc Spoon,} Lex and {\sc Venners,} Bill. How to Write an Equality Method in Java. Aritma Developer, June 2009.\\
	\url{http://www.artima.com/lejava/articles/equality.html}
	
\end{thebibliography}